Variational Monte Carlo on bosonic systems

### 2018-03-21 project_1/article/article.tex
Add table of contents
Add tables and figure
        The article looks insane. This needs to be fixed after adding
        all results.

% It's nice to be able to write your own name
\usepackage[T1]{fontenc}
% Automatic clickable links
\usepackage{hyperref}
% SI-units
\usepackage{siunitx}
% Enhanced math formatting
\usepackage{amsmath}
% Extended math symbols
\usepackage{amssymb}
% Include proof environment
\usepackage{amsthm}
% Import physics package to include bra-ket
\usepackage{physics}
\usepackage{enumerate}
% Import the tensor package for tensors
\usepackage{tensor}
% Include dod and dpd fracs
\usepackage{commath}
% Include font for the identity operator
\usepackage{dsfont}
% Include Tikz
\usepackage{tikz}
% Tikz add-on
\usetikzlibrary{shapes,arrows}
\usetikzlibrary{positioning}
% Several figures in the same figure
\usepackage{subfig}
% Appendix
\usepackage[toc, page]{appendix}

@@

\maketitle

%\begin{widetext}

%\end{widetext}

@@

    \begin{table}
        \centering
        \caption{One particle in one dimension for the numeric expression with
        $2^{21}$ Monte Carlo cycles and a step length of $0.5$.}
        \begin{ruledtabular}
            \begin{tabular}{cccccc}
                $\alpha$ & $\langle  E_L\rangle$ & $\sigma$ & $\sigma_b$
                & $A$&$t_{\text{CPU}} [\si{\second}]$ \\
                \hline
                0.30000&0.56675&0.00026&0.00135&0.89098&0.52634\\
                0.34000&0.53714&0.00019&0.00096&0.88479&0.52186\\
                0.38000&0.51836&0.00013&0.00062&0.87820&0.52351\\
                0.42000&0.50717&0.00009&0.00038&0.87180&0.52892\\
                0.46000&0.50184&0.00004&0.00017&0.86581&0.51759\\
                0.50000&0.50000&0.00001&0.00001&0.86024&0.52427\\
                0.54000&0.50133&0.00004&0.00015&0.85520&0.52052\\
                0.58000&0.50520&0.00007&0.00028&0.84971&0.52156\\
                0.62000&0.51120&0.00011&0.00039&0.84481&0.51830\\
                0.66000&0.51896&0.00014&0.00052&0.83990&0.51865\\
                0.70000&0.52794&0.00017&0.00061&0.83506&0.51255\\
            \end{tabular}
        \end{ruledtabular}
        \label{tab:1D1N_numeric}
    \end{table}

@@

>>>>

% It's nice to be able to write your own name
\usepackage[T1]{fontenc}
% Automatic clickable links
\usepackage{hyperref}
% SI-units
\usepackage{siunitx}
% Enhanced math formatting
\usepackage{amsmath}
% Extended math symbols
\usepackage{amssymb}
% Include proof environment
\usepackage{amsthm}
% Import physics package to include bra-ket
\usepackage{physics}
\usepackage{enumerate}
% Import the tensor package for tensors
\usepackage{tensor}
% Include dod and dpd fracs
\usepackage{commath}
% Include font for the identity operator
\usepackage{dsfont}
% Include Tikz
\usepackage{tikz}
% Tikz add-on
\usetikzlibrary{shapes,arrows}
\usetikzlibrary{positioning}
% Several figures in the same figure
\usepackage{subfig}
%% Appendix
%\usepackage[toc, page]{appendix}

@@

\maketitle
\tableofcontents

@@

    \begin{table}
        \centering
        \caption{One particle in one dimension for the numeric expression with
        $2^{21}$ Monte Carlo cycles and a step length of $0.5$.}
        \begin{ruledtabular}
            \begin{tabular}{cccccc}
                $\alpha$ & $\langle  E_L\rangle$ & $\sigma$ & $\sigma_b$
                & $A$&$t_{\text{CPU}} [\si{\second}]$ \\
                \hline
                0.30&0.56675&0.00026&0.00135&0.89098&0.52634\\
                0.34&0.53714&0.00019&0.00096&0.88479&0.52186\\
                0.38&0.51836&0.00013&0.00062&0.87820&0.52351\\
                0.42&0.50717&0.00009&0.00038&0.87180&0.52892\\
                0.46&0.50184&0.00004&0.00017&0.86581&0.51759\\
                0.50&0.50000&0.00001&0.00001&0.86024&0.52427\\
                0.54&0.50133&0.00004&0.00015&0.85520&0.52052\\
                0.58&0.50520&0.00007&0.00028&0.84971&0.52156\\
                0.62&0.51120&0.00011&0.00039&0.84481&0.51830\\
                0.66&0.51896&0.00014&0.00052&0.83990&0.51865\\
                0.70&0.52794&0.00017&0.00061&0.83506&0.51255\\
            \end{tabular}
        \end{ruledtabular}
        \label{tab:1D1N_numeric}
    \end{table}

@@

    \subsection{Interacting elliptical harmonic oscillator}
        \begin{table}
            \caption{In this table we show the expected energy, the standard
            deviation, the acceptance ratio and the time spent for each $alpha$
            for the elliptical potential with the interacting wavefunction. We
            have used importance sampling with $\delta t = 0.1$ and $2^{21}$
            Monte Carlo cycles and an additional $10\%$ of that as
            thermalization steps. The hard sphere radius is set to $0.0043$ and
            a $\beta = \lambda = \sqrt{8}$.}
            \centering
            \begin{ruledtabular}
                \begin{tabular}{ccccc}
                    $\alpha$ & $\langle  E_L\rangle$ & $\sigma_b$
                    &$A$&$t_C$ \\
                    \hline
                    0.2&35.17548&0.05399&0.98995&24.48868\\
                    0.3&27.62004&0.02311&0.98187&13.65132\\
                    0.4&24.97850&0.00827&0.97248&13.54666\\
                    0.5&24.39877&0.00030&0.96140&13.38388\\
                    0.6&24.83863&0.00604&0.94998&13.31570\\
                    0.7&25.82855&0.01059&0.93766&13.20579\\
                    0.8&27.22895&0.01436&0.92375&13.11933\\
                \end{tabular}
            \end{ruledtabular}
            \label{tab:10_interacting}
        \end{table}

        \begin{table}
            \caption{BLEH}
            \centering
            \begin{ruledtabular}
                \begin{tabular}{ccccc}
                    $\alpha$ & $\langle  E_L\rangle$ & $\sigma_b$
                    &$A$&$t_C$ \\
                    \hline
                    0.2&181.69371&0.25533&0.98756&199.95366\\
                    0.3&142.61591&0.10782&0.97849&195.80928\\
                    0.4&129.88615&0.04051&0.96862&190.44553\\
                    0.5&127.29926&0.00595&0.95749&195.10368\\
                    0.6&129.97630&0.03300&0.94595&193.22755\\
                    0.7&135.67382&0.05785&0.93330&191.96391\\
                    0.8&143.23238&0.07286&0.92061&192.72399\\
                \end{tabular}
            \end{ruledtabular}
            \label{tab:50_interacting}
        \end{table}

        \begin{table}
            \caption{BLEH}
            \centering
            \begin{ruledtabular}
                \begin{tabular}{ccccc}
                    $\alpha$ & $\langle  E_L\rangle$ & $\sigma_b$
                    &$A$&$t_C$ \\
                    \hline
                    0.2&375.04401&0.51475&0.98527&745.21438\\
                    0.3&296.76879&0.20214&0.97534&741.04425\\
                    0.4&270.60830&0.08113&0.94522&723.06823\\
                    0.5&266.37263&0.02020&0.95314&702.71000\\
                    0.6&272.51171&0.07366&0.94112&689.12862\\
                    0.7&285.10285&0.11381&0.92895&707.48248\\
                    0.8&301.40609&0.15458&0.91648&707.86118\\
                \end{tabular}
            \end{ruledtabular}
            \label{tab:100_interacting}
        \end{table}

        \begin{figure}
            \includegraphics[width=250px]{../data/figures/problem_e.pdf}
            \caption{BLEH}
            \label{fig:interacting}
        \end{figure}
